---
title: "Sample Dashboard"
author: "Your Name"
date: "Date"
output: flexdashboard::flex_dashboard
---

```{r setup, include=FALSE}
library(tidyverse)
library(DT)
```

```{r}
mpg_manufacturer <- mpg %>%
  group_by(manufacturer) %>%
  summarize(avg_hwy = mean(hwy, na.rm = TRUE)) %>%
  arrange(desc(avg_hwy))
```

# Name of first page

## Name of first column on page 1

### Ranking of manufacturers by highway fuel efficiency

```{r}
datatable(mpg_manufacturer)
```

## Name of second column on page 1

### Visualization of various manufacturers' highway efficiencies

```{r}
ggplot(data = mpg) +
  geom_boxplot(mapping = aes(x = manufacturer, y = hwy)) +
  coord_flip()
```

# Name of second page

## Column 1 on page 2

### The full `mpg` datatable

```{r}
datatable(mpg)
```

### Plot of `hwy` vs `displ`

```{r}
ggplot(data = mpg) +
  geom_point(mapping = aes(x = displ, y = hwy))
```

## Column 2 on page 2

### Plot of `cty` vs `class`

```{r}
ggplot(data = mpg) +
  geom_boxplot(mapping = aes(x = class, y = cty))
```

### Average highway mileage for each class

```{r}
class_mileage <- mpg %>%
  group_by(class) %>%
  summarize(avg_hwy = mean(hwy, na.rm = TRUE))

datatable(class_mileage)
```

### Visualization of previous row

```{r}
ggplot(data = mpg) +
  geom_boxplot(mapping = aes(x = class, y = hwy))
```


# Name of third page